NYC Spatial Models - Comparison of Spatial Models With and Without Twitter Data

### 2018-11-02 NYC_Twitter_SDM_models - Copy.Rmd
Replace multiple scripts with a single function

Calculate the logsum given a tracts and parks dataset. `tracts$park_ls1` uses only size and distance parameters. `tracts$park_ls2` uses size, distance and tweet parameters. `tracts$park_ls4` and `tracts$park_ls5` use a distance parameter of -15.
```{r accessibility}
source('size00001dist5.R', echo=TRUE)
tracts$park_ls1 <- calculate_park_logsums(tracts, parks, betas = c(.00001, -5))

source('size00001dist5tweet001.R', echo=TRUE)
tracts$park_ls2 <- calculate_park_logsums(tracts, parks, betas = c(.00001, -5, .001))

#source('size00001dist5tweetneg001.R', echo=TRUE)
#tracts$park_ls3 <- calculate_park_logsums(tracts, parks, betas = c(.00001, -5, -.001))

source('size00001dist15.R', echo=TRUE)
tracts$park_ls4 <- calculate_park_logsums(tracts, parks, betas = c(.00001, -15))

source('size00001dist15tweet001.R', echo=TRUE)
tracts$park_ls5 <- calculate_park_logsums(tracts, parks, betas = c(.00001, -15, .001))
```

>>>>

Instead of keeping those functions in separate scripts, we are going to put
everything right here in the document.

```{r logsumfunction}

#' Calculate destination choice logsums from a distance matrix
#' 
#' @param tracts A spatial points dataframe containing $n$
#'   tract geographic information and their attributes.
#' @param parks A spatial points dataframe containing $p$
#'   park geographic information and their attributes.
#' @param distances An $n\times p$ matrix with the distance from all tracts to
#'   all parks in miles.
#' @param sizes A p-length vector of park sizes
#' @param tweets A p-length vector of tweets at parks
#' @param betas A vector containing the size, distance, and tweet coefficients. 
#'   If we submit two variables the tweets are ignored.
#'   
#' @return An n-length vector containing the weighted log-sum based
#'   accessibility between a tract and all parks.
#' @details If we have n tracts and p parks, distances needs to be a 
#' 
calculate_park_logsums <- function(tracts, parks, distances, sizes, tweets = NULL,
                                   betas = c(.00001, -15, .001)){

  # A is n x p
  a <- betas[2] * distances

  # B is p x 1
  b <- betas[1] * sizes

  if(!is.null(tweets)) 
    b <- b + betas[3] * tweets

  # calculate observed utility by adding the weighted park-level attributes 
  # to the columns of the matrix
  # V is n x p, with b added by-column to each element in a
  V <- sweep(a, MARGIN = 2, b, `+`)

  # log-sum of exponentiated utility, Output is n-length vector
  log(rowSums(exp(V)))

}
```

Calculate the logsum given a tracts and parks dataset. `tracts$park_ls1` uses
only size and distance parameters. `tracts$park_ls2` uses size, distance and
tweet parameters. `tracts$park_ls4` and `tracts$park_ls5` use a distance
parameter of -15.
```{r accessibility}
# calculate centroids of tracts and parks
tract_centroids <- gCentroid(tracts, byid = TRUE) 
park_centroids <- gCentroid(parks, byid = TRUE)

# distances from all tracts to all zones
distances <- gDistance(park_centroids, tract_centroids, byid = TRUE) / 5280

tracts$park_ls1 <- calculate_park_logsums(tracts, parks, distances,
                                          parks$Park_Acres, betas = c(.00001, -5))

tracts$park_ls2 <- calculate_park_logsums(tracts, parks, distances, 
                                          parks$Park_Acres, parks$TWEET_COUNT, 
                                          betas = c(.00001, -5, .001))

tracts$park_ls4 <- calculate_park_logsums(tracts, parks, distances, 
                                          parks$Park_Acres, betas = c(.00001, -15))

tracts$park_ls5 <- calculate_park_logsums(tracts, parks, 
                                          parks$Park_Acres, parks$TWEET_COUNT, 
                                          betas = c(.00001, -15, .001))
```
